Developmental trajectories of word recognition: a priming study in bilinguals

### 2023-11-01 manuscript/manuscript.qmd
Simplify gaze functions and clean repository

```{r fig-ptlt-recognition}
#| label: fig-ptlt-recognition-aggr
#| fig-cap: "Average probability of target looking across the time course of the trial. Points an whiskers indicate the mean and standard error of the mean."
data_time |> 
	summarise(.prop = mean(.prop),
			  .by = c(lp, timebin, session_id)) |> 
	ggplot(aes(timebin, .prop, colour = lp)) +
	facet_wrap(~lp, nrow = 1, scales = "free_x") +
	geom_line(aes(group = session_id),
			  # colour = "grey",
			  alpha = 1/10) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	stat_summary(fun.data = "mean_se",
				 geom = "errorbar",
				 width = 0.35,
				 linewidth = 2/4) +
	stat_summary(fun = "mean",
				 geom = "point",
				 size = 1.2) +
	stat_summary(fun = "mean",
				 geom = "line",
				 linewidth = 2/4) +
	labs(x = "Time (ms)",
		 y = "PTLT") +
	scale_x_continuous(breaks = seq(0, 20, 2),
					   labels = \(x) format(x*100+200, big.mark = ",")) +
	scale_y_continuous(labels = scales::percent,
					   breaks = seq(0, 1, 0.2),
					   limits = c(0, 1)) +
	theme(panel.grid.major.y = element_line(colour = "grey",
											linetype = "dotted"),
		  legend.position = "none")
```

@@

@@

>>>>

```{r fig-ptlt-recognition}
#| label: fig-ptlt-recognition-aggr
#| fig-cap: "Average probability of target looking across the time course of the trial. Points an whiskers indicate the mean and standard error of the mean."
#| fig-width: 11
#| fig-height: 4
data_time |> 
	drop_na(.prop) |> 
	summarise(.prop = mean(.prop),
			  .by = c(lp, timebin, session_id)) |> 
	ggplot(aes(timebin, .prop, colour = lp)) +
	facet_wrap(~lp, nrow = 1, scales = "free_x") +
	geom_line(aes(group = session_id),
			  # colour = "grey",
			  alpha = 1/10) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	stat_summary(fun.data = "mean_se",
				 geom = "errorbar",
				 width = 0.35,
				 linewidth = 2/4) +
	stat_summary(fun = "mean",
				 geom = "point",
				 size = 1.2) +
	stat_summary(fun = "mean",
				 geom = "line",
				 linewidth = 2/4) +
	labs(x = "Time (ms)",
		 y = "PTLT") +
	scale_x_continuous(breaks = seq(0, 20, 2),
					   labels = \(x) format(x*100+300, big.mark = ",")) +
	scale_y_continuous(labels = scales::percent,
					   breaks = seq(0, 1, 0.2),
					   limits = c(0, 1)) +
	theme(panel.grid.major.y = element_line(colour = "grey",
											linetype = "dotted"),
		  legend.position = "none")
```

```{r fig-ptlt-recognition-age}
#| label: fig-ptlt-recognition-age
#| fig-cap: "Average probability of target looking across the time course of the trial. Points an whiskers indicate the mean and standard error of the mean."
#| fig-width: 11
#| fig-height: 4
data_time |> 
	summarise(.prop = mean(.prop),
			  .by = c(lp, timebin, age_group, session_id)) |> 
	ggplot(aes(timebin, .prop, colour = age_group)) +
	facet_wrap(~lp, nrow = 1, scales = "free_x") +
	# geom_rug(aes(x = timebin[is.na(.prop)])) +
	# geom_line(aes(group = session_id),
	# 		  alpha = 1/8) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	stat_summary(fun.data = "mean_se",
				 geom = "errorbar",
				 width = 0.4,
				 linewidth = 3/4) +
	stat_summary(fun = "mean",
				 geom = "point",
				 size = 1.2) +
	stat_summary(fun = "mean",
				 geom = "line",
				 linewidth = 3/4) +
	labs(x = "Time (ms)",
		 y = "PTLT",
		 colour = "Age") +
	scale_x_continuous(breaks = seq(0, 20, 4),
					   labels = \(x) format(x*100+200, big.mark = ",")) +
	scale_y_continuous(labels = scales::percent,
					   limits = c(0.40, 0.75),
					   breaks = seq(0, 1, 0.1)) +
	theme(legend.position = "top",
		  panel.grid.major.y = element_line(colour = "grey",
		  								  linetype = "dotted"))
```

@@

```{r fig-ptlt-recognition-condition}
#| label: fig-ptlt-recognition-condition
#| fig-cap: "Average probability of target looking across the time course of the trial. Points an whiskers indicate the mean and standard error of the mean."
#| fig-width: 11
#| fig-height: 4
data_time |> 
	summarise(.prop = mean(.prop),
			  .by = c(lp, timebin, condition, session_id)) |> 
	ggplot(aes(timebin, .prop, colour = condition)) +
	facet_grid(~lp) +
	# geom_rug(aes(x = timebin[is.na(.prop)])) +
	# geom_line(aes(group = interaction(condition, session_id)),
	# 		  alpha = 1/8) +
	geom_hline(yintercept = 0.5, linetype = "dashed") +
	stat_summary(fun.data = "mean_se",
				 geom = "errorbar",
				 width = 0.35,
				 linewidth = 2/4) +
	stat_summary(fun = "mean",
				 geom = "point",
				 size = 1.2) +
	stat_summary(fun = "mean",
				 geom = "line",
				 linewidth = 2/4) +
	labs(x = "Time (ms)",
		 y = "PTLT",
		 colour = "Condition") +
	scale_x_continuous(breaks = seq(0, 20, 4),
					   labels = \(x) format(x*100+200, big.mark = ",")) +
	scale_y_continuous(labels = scales::percent,
					   breaks = seq(0, 1, 0.05)) +
	theme(legend.position = "top",
		  panel.grid.major.y = element_line(colour = "grey",
		  								  linetype = "dotted"))
```

@@

In a first analysis, we examined the effect of phonological priming. We compared participants' looking preference for the target in related and unrelated trials. We first compared the aggregated probability of target looking across time bins in both conditions for each language group.

```{r fig-related-aggregated}
#| label: fig-related-aggregated
#| fig-cap: "A) Aggregated probability of target looking for related and unrelated trials. Each point represents the mean probability of target looking for one participant in one testing session. Lines link observations from the same testing session across conditions. Black dots and errorbars indicate the mean and 95% CrI. B) Aggregated probability of target looking across ages for related and unrelated trials. Lines and error bands indicate the mean and standard error of the mean."
#| fig-width: 10
#| fig-height: 7.5
plot_agg_epreds <- function(newdata, object) {

	epreds <- add_epred_draws(newdata = newdata,
							  object = object,
							  re_formula = NA)
	return(mean_qi(epreds))
}

voc_values <- c(0.25, 0.5, 0.75, 1.00)
age_values <- c(21, 25, 30)

nd_0 <- expand(data_aggr, lp, condition, age = age_values)
nd_1 <- expand(data_aggr, lp, condition, voc_l1 = voc_values)
nd_2 <- expand(data_aggr, lp, condition, voc_total = voc_values)

epreds <- map2(.x = list(nd_0, nd_1, nd_2),
			   .y = model_fits_aggr,
			   .f = plot_agg_epreds) |> 
	map(\(x) {
		mutate(x, 
			   across(matches("voc"),
			   	   \(x) factor(x = x, 
			   	   			levels = voc_values,
			   	   			labels = scales::percent(voc_values))),
			   across(matches("age"),
			   	   \(x) factor(x = x,
			   	   			levels = age_values,
			   	   			labels = age_values)))
	}) |> 
	map(\(x) rename_with(x, \(x) gsub("age|voc_total|voc_l1", "var", x))) |> 
	set_names(names(model_fits_aggr))

plot_epreds <- function(data, x) {
	data |> 
		ggplot(aes(var, .epred, 
				   colour = condition,
				   fill = condition)) +
		facet_wrap(~lp, scales = "free_x") +
		geom_hline(yintercept = 0,
				   linetype = "dashed") +
		geom_errorbar(aes(ymin = .lower,
						  ymax = .upper),
					  width = 0.5,
					  linewidth = 3/4,
					  position = position_dodge(width = 0.5)) +
		geom_point(position = position_dodge(width = 0.5),
				   size = 2)
}

plot_epreds(epreds$fit_aggr_0) +
	labs(x = "Age (months)") +
	plot_epreds(epreds$fit_aggr_1) +
	labs(x = "L1 vocabulary size") +
	theme(strip.text = element_blank()) +
	plot_epreds(epreds$fit_aggr_2) +
	theme(strip.text = element_blank()) +
	labs(x = "Total vocabulary size") +
	plot_layout(ncol = 1, guides = "collect") &
	labs(y = "Logit (Target looking)",
		 colour = "Condition",
		 fill = "Condition") &
	theme(legend.position = "top",
		  panel.grid.major.y = element_line(colour = "grey",
		  								  linetype = "dotted"))

ggsave(file.path("img", "model-agg.jpeg"),
	   height = 7.5, width = 10,
	   dpi = 800)
```

## Time course analysis
